% Sample Resume Template
\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}

\begin{center}
    {\LARGE \textbf{John Doe}}\\[0.3cm]
    Email: john.doe@example.com | Phone: (555) 123-4567\\
    LinkedIn: linkedin.com/in/johndoe | GitHub: github.com/johndoe
\end{center}

\section{Summary}
Experienced software engineer with 5 years of experience in full-stack development. Skilled in Python, JavaScript, and cloud technologies. Passionate about building scalable applications and solving complex problems.

\section{Experience}

\subsection{Senior Software Engineer | Tech Company Inc.}
\textit{January 2021 - Present}

\begin{itemize}[leftmargin=*]
    \item Developed and maintained microservices architecture serving 1M+ users
    \item Led a team of 4 engineers in delivering critical features
    \item Improved system performance by 40\% through optimization
    \item Implemented CI/CD pipelines reducing deployment time by 60\%
\end{itemize}

\subsection{Software Engineer | Startup Solutions}
\textit{June 2019 - December 2020}

\begin{itemize}[leftmargin=*]
    \item Built RESTful APIs using Python and Flask
    \item Designed and implemented database schemas in PostgreSQL
    \item Collaborated with cross-functional teams in Agile environment
    \item Mentored junior developers and conducted code reviews
\end{itemize}

\section{Education}

\subsection{Bachelor of Science in Computer Science}
University of Technology | 2015 - 2019

\begin{itemize}[leftmargin=*]
    \item GPA: 3.8/4.0
    \item Relevant Coursework: Data Structures, Algorithms, Database Systems, Software Engineering
\end{itemize}

\section{Skills}

\textbf{Programming Languages:} Python, JavaScript, TypeScript, Java, SQL

\textbf{Frameworks \& Libraries:} React, Node.js, Django, Flask, Express.js

\textbf{Tools \& Technologies:} Docker, Kubernetes, AWS, Git, Jenkins, PostgreSQL, MongoDB

\textbf{Soft Skills:} Team Leadership, Problem Solving, Communication, Agile Methodologies

\section{Projects}

\subsection{E-Commerce Platform}
Developed a full-stack e-commerce application using React and Node.js. Implemented features including user authentication, product catalog, shopping cart, and payment integration with Stripe.

\subsection{Data Analytics Dashboard}
Built a real-time analytics dashboard using Python and Plotly. Processed and visualized large datasets to provide business insights.

\section{Certifications}
\begin{itemize}[leftmargin=*]
    \item AWS Certified Solutions Architect - Associate
    \item MongoDB Certified Developer
\end{itemize}

\end{document}
